---
output:
  html_document:
    keep_md: true
  pdf_document:
    highlight: tango
    toc: yes
---

```{r config, echo=FALSE}
library(knitr)
opts_chunk$set(background='gray80', tidy=FALSE, 
               cache=FALSE, keep_md=TRUE, 
               fig.path='figure/')
```





# ShowDB Analysis

```{r timeStamp, results='asis'}
Sys.Date()
```


```{r}
library(lubridate)
library(xtable)
library(wesanderson)
```



```{r readData}
# setwd('~/Desktop/showdb/')
sdb <- read.delim('showdb.txt', sep='\t', head=TRUE)
```


```{r explore}
# head(sdb)
dim(sdb)
str(sdb)
```


```{r fixDates}
sdb$ShowDateOriginal <- sdb$ShowDate
sdb$ShowDate <- mdy(sdb$ShowDate)
reCent <- function(x){
  m <- year(x) %% 100
  year(x) <- ifelse(m > 60, 1900+m, 2000+m)
  x
}
sdb$ShowDate <- reCent(sdb$ShowDate)
```

```{r cutNAs}
sdb <- sdb[which(!is.na(sdb$ShowDate)), ]
dim(sdb)
```

```{r}
nrow(sdb[which(sdb$City == '' | sdb$State == ''), c(1:4)])
```


```{r}
names(sdb)
```


```{r}
levels(sdb$Artist)
gd <- sdb[sdb$Artist == 'Grateful Dead', ]
ph <- sdb[sdb$Artist == 'Phish', ]
jgb <- sdb[sdb$Artist == 'Jerry Garcia', ]
dim(gd); dim(ph); dim(jgb)
```



```{r exploreGDDates}
gd <- gd[order(gd$ShowDate), ]
nonShows <- c(grep('rehearsal', gd$Comment, ignore.case=TRUE), 
  grep('Studio', gd$Comment, ignore.case=TRUE), 
  grep('recording', gd$Comment, ignore.case=TRUE))
gd <- gd[-nonShows, ]
dates <- range(gd$ShowDate)
wholeRange <- seq(ymd(dates[1]), ymd(dates[2]),by='days')
```

```{r plotGDDates, fig.height=3, fig.width=12}
plot(wholeRange, 1:length(wholeRange), type='n', ann=FALSE, 
     yaxt='n', xaxt='n')
axis(1, at=seq(ymd('1961-1-1'), ymd('1996-1-1'), by='years'), seq(1961, 1996, 1))
abline(v=gd$ShowDate)
```





```{r uniqueGDSongs}
delim <- "\\ \\-\\ E\\:\\ |E\\:\\ |E\\:|\\, |\\,|\\->\\ \\ |\\->\\ |\\->|\\ \\>\\ "

gd$Set1Clean <- gsub('\\*', '', gd$Set1)
gd$Set2Clean <- gsub('\\*', '', gd$Set2)
gd$Set3Clean <- gsub('\\*', '', gd$Set3)
gd$allCleanSets <- paste(gd$Set1Clean, gd$Set2Clean, gd$Set3Clean)
allSets <- c(gd$Set1Clean, gd$Set2Clean, gd$Set3Clean)
allSongs <- unlist(strsplit(as.character(allSets), delim))
allUniqueSongs <- sort(unique(allSongs))
length(allSongs)-1577  # minus blank entries

## Unique Songs - used for debugging dataset
# cbind(allUniqueSongs)
```

```{r topSongsTable}
times <- matrix(0, nrow(gd), length(allUniqueSongs))
dimnames(times)[2] <- list(allUniqueSongs)
times[1:5, 1:5]
#cbind(dimnames(times)[[2]])
times <- times[, -c(1, 2, 4)]
times <- times[, -c(which(colnames(times) %in% 
                            c('', 
                              '?', 
                              '<technical difficulties>?',
                              'Rain')))]
times[1:5, 1:5]

for (i in 1:ncol(times)) {
  song <- dimnames(times)[[2]][i]
  found <- grep(song, gd$allCleanSets)
  times[found, i] <- 1
  }
# rowSums(times) 
# sort(colSums(times))
times <- times[, order(colSums(times), decreasing=FALSE)]
counts <- data.frame(times=colSums(times), index=(ncol(times):1))
countsSort <- counts[order(counts$index), ]
# sum(counts$times)
```

```{r countsReadOut, results='asis'}
print(xtable(countsSort), type='html')
```


```{r plotSongs, fig.height=10, fig.width=12}
plot(wholeRange, 1:length(wholeRange), type='n', ann=FALSE, 
     yaxt='n', xaxt='n', bty='n', ylim=c(1,ncol(times)))
axis(1, at=seq(ymd('1961-1-1'), ymd('1996-1-1'), by='years'), seq(1961, 1996, 1))
abline(v=gd$ShowDate, col='gray92')
for(i in ncol(times):1) {
  points(gd$ShowDate, rep(i, nrow(gd)), pch='.', cex=times[, i]*2, col='tomato')
  }
```


sort(table(gd$ShowDate))

1975 looks like all rehersal and recording? Look for them here: [dead.net](http://www.dead.net/shows?page=45)


```{r getIntroDateOrder}
timesBig <- times
times <- times[, which(colSums(times) > 1)]
ncol(times)  # songs
nrow(times)  # dates
rleSongs <- apply(times, 2, 'rle')
introDate <- rep(0, ncol(times))
for (i in 1:ncol(times)) {
  introDate[i] <- rleSongs[[i]]$lengths[1]
  }
timesIntroOrder <- times[, rev(order(introDate))]
```


```{r getMarginDensity}
timesIntroOrderNonzero <- timesIntroOrder[which(rowSums(timesIntroOrder) > 0), ]
dens <- rep(0, ncol(timesIntroOrderNonzero))
rleOrdered <- apply(timesIntroOrderNonzero, 2, 'rle')
for(i in 1:length(dens)) {
  vect <- timesIntroOrderNonzero[, i]
  vect2 <- vect[rleOrdered[[i]]$lengths[1]:length(vect)]
  dens[i] <- mean(vect2)
  }
```

dens
plot(dens, type='l')
points(loess.smooth(1:length(dens), dens, degree=10), type='l')
plot(loess.smooth(1:length(dens), dens, degree=2, span=.7), type='l')

```{r plotSongsIntroOrder, fig.height=10, fig.width=12}
par(mar=c(5, 1, 1, 10))
plot(wholeRange, 1:length(wholeRange), type='n', ann=FALSE, yaxs='i',
     yaxt='n', xaxt='n', bty='n', ylim=c(1,ncol(times)))
axis(1, at=seq(ymd('1961-1-1'), ymd('1996-1-1'), by='years'), seq(1961, 1996, 1), las=2)
abline(v=gd$ShowDate, col='gray92')
for(i in ncol(timesIntroOrder):1) {
  points(gd$ShowDate, rep(i, nrow(gd)), pch='.', cex=timesIntroOrder[, i]*2, col='tomato')
  }
```


dim(timesIntroOrder)
abline(h=250)
abline(h=263)
abline(h=235)
colnames(timesIntroOrder)[250:263]
colnames(timesIntroOrder)

dim(times)
dim(times[, which(colSums(times) < 2)])

gd[grep('Rehearsal', gd$Comment), ]


gd[unique(nonShows), 1:4]

head(gd)




